---
title: "Rspotify"
author: "Bui Thai Hiep"
date: "9/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages
```{r}
pacman::p_load("devtools"
               , "jsonlite"
               , "dplyr"
               , "tidyr"
               , "Rspotify"
               , "spotifyr"
               , "sqldf")
```
Getting keys from Spotify using Rspotify
```{r}
keys <- spotifyOAuth(app_id = "My Rspotify Project", #whatever I would like
                     client_id = "a0299cfb25944ecdbffc9079b987ff9a", # From spotify
                     client_secret = "f773ae310efa4f74a751bb6f50d4b0b4" ) # From spotify
```
Set up for Spotifyr
```{r}
Sys.setenv(SPOTIFY_CLIENT_ID = 'a0299cfb25944ecdbffc9079b987ff9a')
Sys.setenv(SPOTIFY_CLIENT_SECRET = 'f773ae310efa4f74a751bb6f50d4b0b4')

access_token <- get_spotify_access_token()
```
Information about a user
```{r}
user <- getUser(user_id = 11138689754 # From spotify profile
                ,token = keys)
```

Loading data received from spotify
```{r}
address <- "/Users/tomasbui/Library/Mobile Documents/com~apple~CloudDocs/Downloads/MyData/StreamingHistory"
file_type <- ".json"

paths <- list()
for (i in seq(1,6)){
  paths[[i]] <- paste(address, i-1, file_type, sep = "")
}

list_df <- list()
df <- data.frame()
for (i in seq(from = 1, to = length(paths))) {
  print(paths[[i]])
  list_df[[i]] <- jsonlite::fromJSON(txt = paths[[i]], flatten = TRUE)
  #assign(paste0("Stream_history_", i), as.data.frame(list_df[[i]])) # if each list should be saved as a separate dataframe
}
df <- do.call(rbind, list_df)
tail(df)
```
From df we can see name of the artist, which song, how long it was played and time when the song finished 

Select an artist and check if it is in the dataset
```{r}
artist <- 'Stromae'
ifelse ((df %>% 
          filter(artistName == artist) %>% 
          select(artistName) %>% 
          unique() == artist)[1]
        , yes = 'Artist present in the list.'
        , no = 'Artist not present in the list. Select a different one')
```

Check for a songs of the selected artists in the my playlist and select song called cheese
```{r}
df %>% head()
track <- df %>% 
  filter(artistName == artist) %>% 
  group_by(trackName) %>% 
  summarise(TotalTimePlayed = sum(msPlayed)) %>% 
  arrange(TotalTimePlayed) %>% 
  filter(trackName == 'Cheese') %>% 
  select(1)
track
```

Get information about the selected song 
```{r}
# all songs with word 'cheese' in the name
cheese_songs <- search_spotify(q = unlist(track), type = 'track')
# selecting the id of the album the songs belong to
all_album_id <- cheese_songs %>% 
  select(album.id)
```
search for artists with the name selected
```{r}
artist_info <- search_spotify(q = artist, type = 'artist')
artist_id <- artist_info %>% 
  select(id, name)
```
Search for a match between the album having selected song and all available albums of a selected artist
```{r}
# selected artist -> all available albums -> album ids of the selected artist
artist_album <- get_artist_albums(id = artist_id[1,1])
selected_artist_albums_id <- artist_album %>% 
  select(id)

#finding a match between all available albums and the selected artists album
album_id_match <- sqldf('SELECT *
                         FROM all_album_id 
                         INTERSECT 
                         SELECT * 
                         FROM selected_artist_albums_id')

# the matched album 
album_id_match

track_id <- cheese_songs %>% 
  filter(album.id == unlist(album_id_match)) %>% 
  select(id)
```

```{r}
searchArtist(artist, token = keys)
```

